Checking Invariant Confluence, In Whole or In Parts \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-06-14 doc/sigmod_paper/sections/interactive_decision_procedure.tex
Joe feedback.
Cleaned up commented out text.
Got rid of orphaned text.

\IsInvConfluent{} assumes access to an \invariantclosure{} decision procedure
\IsIclosed$(O, I)$. \IsIclosed$(O, I)$ returns a triple (closed, $s_1$, $s_2$).
closed is a boolean indicating whether $O$ is \Iclosed{}. If closed is true,
then $s_1$ and $s_2$ are null. If closed is false, then $s_1$ and $s_2$ are a
counterexample witnessing the fact that $O$ is not \Iclosed{}. That is,
$I(s_1)$ and $I(s_2)$, but $\lnot I(s_1 \join s_2)$ (e.g., $s_1$ and $s_2$ from
\exampleref{Z2}).  As we mentioned earlier, we can (and do) implement the
\invariantclosure{} decision procedure using an SMT solver like
Z3~\cite{de2008z3}.

@@

If \IsIclosed{} determines that $O$ is \emph{not} \iclosed{(I - NR)}, then we
have a counterexample $s_1, s_2$. We want to determine whether $s_1$ and $s_2$
are reachable or unreachable. We can do so in two ways.
%
First, we can randomly generate a set of reachable states and add them to $R$.
If $s_1$ or $s_2$ is in $R$, then we know they are reachable.
%
Second, we can prompt the user to tell us directly whether or not the states
are reachable or unreachable.

In addition to labelling $s_1$ and $s_2$ as reachable or unreachable, the user
can also refine $I$ by augmenting $R$ and $NR$ arbitrarily (see
\figref{DecisionProcedureExample} for an example). In this step, we also make
sure that $s_0 \notin NR$ since we know that $s_0$ is reachable.

@@

\Helper{} recurses only when one of $s_1$ or $s_2$ is unreachable, so $NR$
grows after every recursive invocation of \Helper{}. Similarly, $R$ continues
to grow as \Helper{} randomly explores the set of reachable states. As the user
sees more and more examples of unreachable and reachable states, it often becomes
easier and easier for them to recognize patterns that define which states are
reachable and which are not. As a result, it becomes easier for a user to
augment $NR$ and eliminate a large number of unreachable states from the
invariant. Once $NR$ has been sufficiently augmented to the point that $I - NR$
is a subset of the reachable states, \thmref{IclosureEquivalentIconfluence}
guarantees that the algorithm will terminate after one more call to \IsIclosed.

% \subsection{Limitations}
% Our interactive \invariantconfluence{} decision procedure has two
% limitations. First, \algoref{InteractiveDecisionProcedure} requires an
% \invariantclosure{} decision procedure, but determining \invariantclosure{} is
% undecidable in general.
% %
% In practice, we can implement an \invariantclosure{} decision procedure using
% an SMT solver like Z3 that works well on simple objects, invariants, and merge
% operators (e.g., integers, tuples, infinite sets, bit vectors, linear
% constraints, basic arithmetic, tuple projection, basic set operations, bit
% arithmetic). But, SMT solvers are mostly unable to analyze more complex
% constructs (e.g., finite lists~\cite{kroning2009proposal}, graphs, recursive
% algebraic data types, nonlinear constraints, merge operators that contain loops
% or recursion).
%
% Second, \algoref{InteractiveDecisionProcedure} relies on a user to identify
% unreachable states. As we saw in \figref{DecisionProcedureExample}, the set of
% unreachable states can sometimes be clear, especially if there's a noticeable
% pattern in the set of reachable states. However, if the set of transactions is
% large or complex or if the merge operator is complex, then reasoning about
% unreachable states can be difficult.  Unlike with reachable states---where
% verifying that a state is reachable only requires thinking of a single way to
% reach the state---verifying that a state is unreachable requires a programmer
% to reason about a large number of system executions and conclude that
% \emph{none} of them can lead to the state. In the future, we plan on exploring
% ways to help a user reason about unreachable states and ways to discover sets of
% unreachable states automatically.

>>>>

\IsInvConfluent{} assumes access to an \invariantclosure{} decision procedure
\IsIclosed$(O, I)$. \IsIclosed$(O, I)$ returns a triple (closed, $s_1$, $s_2$).
closed is a boolean indicating whether $O$ is \Iclosed{}. If closed is true,
then $s_1$ and $s_2$ are null. Otherwise, $s_1$ and $s_2$ are a counterexample
witnessing the fact that $O$ is not \Iclosed{}. That is, $I(s_1)$ and $I(s_2)$,
but $\lnot I(s_1 \join s_2)$ (e.g., $s_1$ and $s_2$ from \exampleref{Z2}).  As
we mentioned earlier, we can (and do) implement the \invariantclosure{}
decision procedure using an SMT solver like Z3~\cite{de2008z3}.

@@

If \IsIclosed{} determines that $O$ is \emph{not} \iclosed{(I - NR)}, then we
have a counterexample $s_1, s_2$. We want to determine whether $s_1$ and $s_2$
are reachable or unreachable. We can do so in two ways.
%
First, we can randomly generate a set of reachable states and add them to $R$.
If $s_1$ or $s_2$ is in $R$, then they are reachable.
%
Second, we can prompt the user to tell us directly whether the states
are reachable or unreachable.

In addition to labelling $s_1$ and $s_2$ as reachable or unreachable, the user
can also refine $I$ by augmenting $R$ and $NR$ arbitrarily (see
\figref{DecisionProcedureExample} for example). In this step, we also make
sure that $s_0 \notin NR$ since we know that $s_0$ is reachable.

@@

\Helper{} recurses only when one of $s_1$ or $s_2$ is unreachable, so $NR$
grows after every recursive invocation of \Helper{}. Similarly, $R$ continues
to grow as \Helper{} randomly explores the set of reachable states. As the user
sees more and more examples of unreachable and reachable states, it often becomes
easier and easier for them to recognize patterns that define which states are
reachable and which are not. As a result, it becomes easier for a user to
augment $NR$ and eliminate a large number of unreachable states from the
invariant. See \figref{DecisionProcedureExample}, for example. Once $NR$ has
been sufficiently augmented to the point that $I - NR$ is a subset of the
reachable states, \thmref{IclosureEquivalentIconfluence} guarantees that the
algorithm will terminate after one more call to \IsIclosed.

### 2020-06-14 doc/sigmod_paper/sections/introduction.tex
Got rid of orphaned text.

\section{Introduction}
When an application designer decides to replicate a piece of data, they have to
make a fundamental choice between weak and strong consistency. Replicating the
data with strong consistency using a technique like distributed
transactions~\cite{bernstein1981concurrency} or state
machine replication~\cite{lamport1998part} makes the application designer's life
very easy. To the developer, a strongly consistent system behaves exactly like
a single-threaded system running on a single node, so reasoning about the
behavior of the system is simple~\cite{herlihy1990linearizability}.
Unfortunately, strong consistency is at odds with performance. The CAP theorem
and PACELC theorem tell us that strongly consistent systems suffer from higher
latency at best and unavailability at worst~\cite{gilbert2002brewer,
abadi2012consistency}. On the other hand, weak consistency
models like eventual consistency~\cite{vogels2009eventually}, PRAM
consistency~\cite{lipton1988pram}, causal consistency~\cite{ahamad1995causal},
and others~\cite{lloyd2011don, mehdi2017can} allow data to be replicated with
high availability and low latency, but they put a tremendous burden on the
application designer to reason about the complex interleavings of operations
that are allowed by these weak consistency models. In particular, weak
consistency models strip an application developer of one of the earliest and
most effective tools that is used to reason about the execution of programs:
application invariants~\cite{balegas2015towards} such as
database integrity constraints~\cite{grefen1993integrity}. Even
if every transaction executing in a weakly consistent system individually
maintains an application invariant, the system as a whole can produce
invariant-violating states.

@@

\textbf{The second main thrust of this paper is to partially avoid coordination
even in programs that require it}, by generalizing \invariantconfluence{} to a
property called \emph{segmented \invariantconfluence{}}. While
\invariantconfluence{} characterizes objects that can be replicated
\emph{without any} coordination, segmented \invariantconfluence{} allows us to
replicate non-\invariantconfluent{} objects with only \emph{occasional}
coordination. The main idea is to divide the set of invariant-satisfying states
into \emph{segments}, with a restricted set of transactions allowed in each
segment. Within a segment, servers act without any coordination; they
synchronize only to transition across segment boundaries. This design
highlights the trade-off between application complexity and
coordination-freedom; more complex applications require more segments which
require more coordination, and vice-versa.

>>>>

\section{Introduction}
When an application designer decides to replicate a piece of data, they have to
make a fundamental choice between weak and strong consistency. Replicating the
data with strong consistency using a technique like distributed
transactions~\cite{bernstein1981concurrency} or state
machine replication~\cite{lamport1998part} makes the application designer's life
very easy. To the developer, a strongly consistent system behaves exactly like
a single-threaded system running on a single node, so reasoning about the
behavior of the system is simple~\cite{herlihy1990linearizability}.
Unfortunately, strong consistency is at odds with performance. The CAP theorem
and PACELC theorem tell us that strongly consistent systems suffer from higher
latency at best and unavailability at worst~\cite{gilbert2002brewer,
abadi2012consistency}. On the other hand, weak consistency
models like eventual consistency~\cite{vogels2009eventually}, PRAM
consistency~\cite{lipton1988pram}, causal consistency~\cite{ahamad1995causal},
and others~\cite{lloyd2011don, mehdi2017can} allow data to be replicated with
high availability and low latency, but they put a tremendous burden on the
application designer to reason about the complex interleavings of operations
that are allowed by these weak consistency models. In particular, weak
consistency models strip an application developer of one of the earliest and
most effective tools that is used to reason about the execution of programs:
application invariants~\cite{hoare1969axiomatic, balegas2015towards} such as
database integrity constraints~\cite{grefen1993integrity}. Even
if every transaction executing in a weakly consistent system individually
maintains an application invariant, the system as a whole can produce
invariant-violating states.

@@

\textbf{The second main thrust of this paper is to partially avoid coordination
even in programs that require it}, by generalizing \invariantconfluence{} to a
property called \emph{segmented \invariantconfluence{}}. While
\invariantconfluence{} characterizes objects that can be replicated
\emph{without any} coordination, segmented \invariantconfluence{} allows us to
replicate non-\invariantconfluent{} objects with only \emph{occasional}
coordination. The main idea is to divide the set of invariant-satisfying states
into \emph{segments}, with a restricted set of transactions allowed in each
segment. Within a segment, servers act without any coordination; they
synchronize only to transition across segment boundaries. This design
highlights the trade-off between application complexity and
coordination-freedom; more complex applications require more segments which
require more coordination.

### 2020-06-14 doc/sigmod_paper/sections/invariant_closure.tex
First round of cuts.
The paper is now 8 pages without citations. We need 8 pages with
citations, so we need to trim another page or so. I'll probably shrink
the evaluation a bit more, shrink the related works a bit more, shrink
segmented invariant confluence a bit more and see what we end up with.
Got rid of orphaned text.

\thmref{IclosureImpliesIconfluence} states that \invariantclosure{} is
sufficient for \invariantconfluence{}. Intuitively, recall that our system model ensures
that transaction execution preserves the invariant, so if merging states also
preserves the invariant and if our start state satisfies the invariant, then
inductively it is impossible for us to reach a state that doesn't satisfy the
invariant.

@@

\begin{example}\examplelabel{Z2}
  Let $O = (\ints \times \ints, \join)$ consist of pairs $(x, y)$ of integers
  where $(x_1, y_1) \join (x_2, y_2) = (\max(x_1, x_2), \max(y_1, y_2))$. Our
  start state $s_0 \in \ints \times \ints$ is the point $(0, 0)$. Our set $T$
  of transactions consists of two transactions: $t_{x+1}((x, y)) = (x + 1, y)$
  which increments $x$ and $t_{y-1}((x, y)) = (x, y - 1)$ which decrements $y$.
  Our invariant $I = \setst{(x, y) \in \ints \times \ints}{xy \leq 0}$ consists
  of all points $(x, y)$ where the product of $x$ and $y$ is non-positive.

@@

In \exampleref{Z2}, $s_1$ and $s_2$ witness the fact that $O$ is not
\invariantclosed{}, but $s_1$ is not reachable. This is not particular to
\exampleref{Z2}. In fact, it is fundamentally the reason why
\invariantclosure{} is not equivalent to \invariantconfluence{}.
\Invariantconfluence{} is, at its core, a property of reachable states, but
\invariantclosure{} is completely ignorant of reachability. As a result,
invariant-satisfying yet unreachable states like $s_1$ are the key hurdle
preventing \invariantclosure{} from being equivalent to \invariantconfluence{}.
This is formalized by \thmref{IclosureEquivalentIconfluence}.

>>>>

\thmref{IclosureImpliesIconfluence} states that \invariantclosure{} is
sufficient for \invariantconfluence{}. Intuitively, our system model ensures
that transaction execution preserves the invariant, so if merging states also
preserves the invariant and if our start state satisfies the invariant, then
inductively it is impossible for us to reach a state that doesn't satisfy the
invariant.

@@

\begin{example}\examplelabel{Z2}
  Let $O = (\ints \times \ints, \join)$ consist of pairs $(x, y)$ of integers
  where $(x_1, y_1) \join (x_2, y_2) = (\max(x_1, x_2), \max(y_1, y_2))$. Our
  start state $s_0 \in \ints \times \ints$ is $(0, 0)$. Our set $T$ of
  transactions consists of two transactions: $t_{x+1}((x, y)) = (x + 1, y)$
  which increments $x$ and $t_{y-1}((x, y)) = (x, y - 1)$ which decrements $y$.
  Our invariant $I = \setst{(x, y) \in \ints \times \ints}{xy \leq 0}$ consists
  of all points $(x, y)$ where the product of $x$ and $y$ is non-positive.

@@

In \exampleref{Z2}, $s_1$ and $s_2$ witness the fact that $O$ is not
\invariantclosed{}, but $s_1$ is \emph{not reachable}. This is not particular to
\exampleref{Z2}. In fact, it is fundamentally the reason why
\invariantclosure{} is not equivalent to \invariantconfluence{}.
\Invariantconfluence{} is, at its core, a property of reachable states, but
\invariantclosure{} is completely ignorant of reachability. As a result,
invariant-satisfying yet unreachable states like $s_1$ are the key hurdle
preventing \invariantclosure{} from being equivalent to \invariantconfluence{}.
This is formalized by \thmref{IclosureEquivalentIconfluence}.

### 2020-06-14 doc/sigmod_paper/sections/invariant_confluence.tex
Got rid of orphaned text.

We begin by introducing our system model of replicated objects in which a
distributed object and accompanying invariant is replicated across a set of
servers. Clients send transactions to servers, and a server executes a
transaction so long as it maintains the invariant. Servers execute
transactions without coordination, but to avoid state divergence, servers
periodically gossip with one another and merge their replicas.
%
After we introduce the system model, we present a formal definition of
\invariantconfluence{}.

@@

@@

In our system model, a distributed object $O$ is replicated across a set $p_1,
\ldots, p_n$ of $n$ servers. Each server $p_i$ manages a replica $s_i \in S$ of
the replicated object. Every server begins with a start state $s_0 \in S$, a
fixed set $T$ of transactions, and an invariant $I$. Servers repeatedly perform
one of two actions.

@@

We say an expression $e$ is \defword{\sTIreachable{}} if it corresponds to a
valid execution of our system model. Formally, we define
$\sTIreachablepredicate{e}$ to be the predicate that satisfies the
following conditions:
\begin{itemize}
  \item
    $\sTIreachablepredicate{s_0}$.
  \item
    For all expressions $e$ and for all transactions $t$ in the set $T$ of
    transactions, if $\sTIreachablepredicate{e}$ and $I(t(e))$, then
    $\sTIreachablepredicate{t(e)}$.
  \item
    For all expressions $e_1$ and $e_2$, if $\sTIreachablepredicate{e_1}$ and
    $\sTIreachablepredicate{e_2}$, then $\sTIreachablepredicate{e_1 \join
    e_2}$.
\end{itemize}
Similarly, we say a state $s \in S$ is \sTIreachable{} if there exists an
\sTIreachable{} expression $e$ that evaluates to $s$. Returning to
\exampleref{Ints} with start state $s_0 = 42$, we see that all integers greater
than or equal to 42 (i.e.\ $\setst{x \in \ints}{x \geq 42}$) are
\sTIreachable{}, and all other integers are \sTIunreachable{}.

>>>>

We begin by introducing our system model of replicated objects in which a
distributed object and an invariant are replicated across a set of
servers. Clients send transactions to servers, and servers execute
transactions so long as they maintain the invariant. Servers execute
transactions without coordination, but to avoid state divergence, servers
periodically gossip with one another and merge their replicas.
%
% After we introduce the system model, we present a formal definition of
% \invariantconfluence{}.

@@

\vfill\null

@@

In our system model, a distributed object $O$ is replicated across a set $p_1,
\ldots, p_n$ of $n$ servers. Each server $p_i$ manages a replica $s_i \in S$ of
the object. Every server begins with a start state $s_0 \in S$, a
fixed set $T$ of transactions, and an invariant $I$. Servers repeatedly perform
one of two actions.

@@

We say an expression $e$ is \defword{\sTIreachable{}} if it corresponds to a
valid execution of our system model. Formally, we define
$\sTIreachablepredicate{e}$ to be the predicate that satisfies the
following conditions:
\pagebreak
\begin{itemize}
  \item
    $\sTIreachablepredicate{s_0}$.
  \item
    For all expressions $e$ and for all transactions $t$ in the set $T$ of
    transactions, if $\sTIreachablepredicate{e}$ and $I(t(e))$, then
    $\sTIreachablepredicate{t(e)}$.
  \item
    For expressions $e_1$ and $e_2$, if $\sTIreachablepredicate{e_1}$ and
    $\sTIreachablepredicate{e_2}$, then $\sTIreachablepredicate{e_1 \join
    e_2}$.
\end{itemize}

Similarly, we say a state $s \in S$ is \sTIreachable{} if there exists an
\sTIreachable{} expression $e$ that evaluates to $s$. Returning to
\exampleref{Ints} with start state $s_0 = 42$, we see that all integers greater
than or equal to 42 (i.e.\ $\setst{x \in \ints}{x \geq 42}$) are
\sTIreachable{}, and all other integers are \sTIunreachable{}.

### 2020-06-14 doc/sigmod_paper/sections/related_work.tex
Polished up paper, now 8 pages.
Joe feedback.
Got rid of orphaned text.

\newcommand{\sieve}{\textsc{SIEVE}}
% \textbf{RedBlue Consistency and \sieve.}
RedBlue consistency is a consistency model that sits between causal consistency
and linearizability~\cite{li2012making}.
%
% With RedBlue consistency, every operation is manually labelled as either red or
% blue. All operations are executed with causal consistency, but with the added
% restrictions that red operations are executed in a single total order embedded
% within the causal ordering.
%
In~\cite{li2012making}, Li et al.\ introduce invariant safety as a
sufficient (but not necessary) condition for RedBlue consistent objects to be
\invariantconfluent{}. Invariant safety is an analog of \invariantclosure{}.
In~\cite{li2014automating}, Li et al.\ develop sophisticated techniques for
deciding invariant safety that involve calculating weakest preconditions.
% These
% techniques are complementary to our work and can be used to improve the
% \invariantclosure{} subroutine used by our decision procedures.
%
% In contrast with these techniques, our \invariantconfluence{} decision
% procedures can determine the \invariantconfluence{} of objects that are
% \emph{not} invariant safe.

@@

% \textbf{Explicit Consistency.}
Explicit consistency~\cite{balegas2015towards} is a consistency model that
combines \invariantconfluence{} and causal consistency, similar to RedBlue
consistency with invariant safety.
% To determine if a workload is amenable to
% explicitly consistent replication, Balegas et al.\ determine if all pairs of
% transactions can be concurrently executed on the same start state without
% violating the invariant~\cite{balegas2015towards}. Balegas et al.\ argue that
% this is a sufficient condition for explicit consistency. It is similar to
% criterion (3) in \thmref{LatticeProperty}. In our work, we take a step further
% and explore sufficient \emph{and necessary} conditions for
% \invariantconfluence{}.
%
Balegas et al.\ also describe a variety of techniques---like conflict
resolution, locking, and escrow transactions~\cite{o1986escrow}---that can be
used to replicate workloads that do not meet their sufficient conditions.
Segmented \invariantconfluence{} is a general-purpose formalism that can be
used to model simple forms of these techniques.

% \textbf{Token Based Invariant Confluence.}
In~\cite{gotsman2016cause}, Gotsman et al.\ discuss a hybrid token based
consistency model that generalizes a family of consistency models including
causal consistency, sequential consistency, and RedBlue consistency.
% An
% application designer defines a set of tokens and specifies which pairs of
% tokens conflict, and transactions acquire some subset of the tokens when they
% execute. This allows the application designer to specify which transactions
% conflict with one another.  Gotsman et al.\ develop sufficient conditions to
% determine whether a given token scheme is sufficient to guarantee that a global
% invariant is never broken.
The token based approach allows users to
specify certain conflicts that are not possible with segmented
\invariantconfluence{} because a segmentation only allows transactions within a
segment to acquire a single self-conflicting lock. However, segmented
\invariantconfluence{} also introduces the notion of invariant segmentation,
which cannot be emulated with the token based approach.
% For example, it is
% difficult to emulate escrow transactions with the token based approach.

>>>>

\newcommand{\sieve}{\textsc{SIEVE}}
RedBlue consistency~\cite{li2012making}, is a consistency model that sits
between causal consistency and linearizability.
%
% With RedBlue consistency, every operation is manually labelled as either red or
% blue. All operations are executed with causal consistency, but with the added
% restrictions that red operations are executed in a single total order embedded
% within the causal ordering.
%
In~\cite{li2012making}, Li et al.\ introduce invariant safety as a
sufficient (but not necessary) condition for RedBlue consistent objects to be
\invariantconfluent{}. Invariant safety is an analog of \invariantclosure{}.
In~\cite{li2014automating}, Li et al.\ develop sophisticated techniques for
deciding invariant safety that involve calculating weakest preconditions.
These techniques are complementary to our work and can be used to improve the
\invariantclosure{} subroutine used by our decision procedures.
%
% In contrast with these techniques, our \invariantconfluence{} decision
% procedures can determine the \invariantconfluence{} of objects that are
% \emph{not} invariant safe.

@@

% \textbf{Explicit Consistency.}
Explicit consistency~\cite{balegas2015towards} is a consistency model that
combines \invariantconfluence{} and causal consistency, similar to RedBlue
consistency with invariant safety.
% To determine if a workload is amenable to
% explicitly consistent replication, Balegas et al.\ determine if all pairs of
% transactions can be concurrently executed on the same start state without
% violating the invariant~\cite{balegas2015towards}. Balegas et al.\ argue that
% this is a sufficient condition for explicit consistency. It is similar to
% criterion (3) in \thmref{LatticeProperty}. In our work, we take a step further
% and explore sufficient \emph{and necessary} conditions for
% \invariantconfluence{}.
%
Balegas et al.\ also describe a variety of techniques---like conflict
resolution, locking, and escrow transactions~\cite{o1986escrow}---that can be
used to replicate workloads that do not meet their sufficient conditions.
Segmented \invariantconfluence{} is a formalism that can be
used to model simple forms of these techniques.

% \textbf{Token Based Invariant Confluence.}
In~\cite{gotsman2016cause}, Gotsman et al.\ discuss a hybrid token based
consistency model that generalizes a family of consistency models including
causal consistency, sequential consistency, and RedBlue consistency.
% An
% application designer defines a set of tokens and specifies which pairs of
% tokens conflict, and transactions acquire some subset of the tokens when they
% execute. This allows the application designer to specify which transactions
% conflict with one another.  Gotsman et al.\ develop sufficient conditions to
% determine whether a given token scheme is sufficient to guarantee that a global
% invariant is never broken.
The token based approach allows users to
specify certain conflicts that are not possible with segmented
\invariantconfluence{}.
% because a segmentation only allows transactions within a
% segment to acquire a single self-conflicting lock.
However, segmented
\invariantconfluence{} also introduces the notion of invariant segmentation,
which cannot be emulated with the token based approach.
For example, it is
difficult to emulate escrow transactions with the token based approach.

### 2020-06-14 doc/sigmod_paper/sections/segmented_invariant_confluence.tex
Got rid of orphaned text.

As before, servers repeatedly perform one of two actions: execute a transaction
or merge states with another server. Merging states in the segmented
\invariantconfluence{} system model is identical to merging states in the
\invariantconfluence{} system model. A server $p_i$ sends its state $s_i$ to
another server $p_j$ which \emph{must} merge $s_i$ into its state $s_j$.
%
Transaction execution in the new system model, on the other hand, is a bit more
involved. Consider a server $s_i$ with active segment $(I_i, T_i)$. A client
can request that $p_i$ execute a transaction $t \in T$. We consider what
happens when $t \in T_i$ and $t \notin T_i$ separately.

@@

Instead, we develop a new decision procedure that can be used to determine if
an object is \sticonfluent{s}{T}{I} for every state $s \in I$. To do so, we
need to extend the notion of reachability to a notion of coreachability and
then generalize \thmref{IclosureEquivalentIconfluence}. Two states $s_1, s_2
\in I$ are \defword{coreachable} with respect to $T$ and $I$, abbreviated
\defword{\TIcoreachable}, if there exists some state $s_0 \in I$ such that
$s_1$ and $s_2$ are both \sTIreachable{}.

@@

  Applying \algoref{InteractiveDecisionProcedure}, \IsIclosed{} returns false
  with the states $s_1 = (1, 0, 0), (0, 1, 0)$ and $s_2 = (1, 0, 0), (0, 0,
  1)$. Both are reachable, so $O$ is not \sTIconfluent{} and
  \algoref{InteractiveDecisionProcedure} returns false.  The culprit is
  concurrent decrements, which we can forbid in a simple one-segment
  segmentation $\Sigma = (I, T^+)$ where $T^+$ consists only of increment
  transactions. Applying \algoref{ArbitraryStartInteractiveDecisionProcedure},
  \IsIclosed{} again returns false with the same states $s_1$ and $s_2$. This time,
  however, the user recognizes that the two states are not
  \ticoreachable{T^+}{I}. The user refines $NR$ with the observation that two
  states are coreachable if and only if they have the same values of $n_1, n_2,
  n_3$. After this, \IsIclosed{} and
  \algoref{ArbitraryStartInteractiveDecisionProcedure} return true.
\end{example}

>>>>

As before, servers repeatedly perform one of two actions: execute a transaction
or merge states with another server. Merging states in the segmented
\invariantconfluence{} system model is identical to merging states in the
\invariantconfluence{} system model. A server $p_i$ sends its state $s_i$ to
another server $p_j$ which \emph{must} merge $s_i$ into its state $s_j$.
%
Transaction execution in the new system model, on the other hand, is more
involved. Consider a server $s_i$ with active segment $(I_i, T_i)$. A client
can request that $p_i$ execute a transaction $t$. We consider what happens when
$t \in T_i$ and when $t \notin T_i$.

@@

Instead, we develop a new decision procedure that can be used to determine if
an object is \sticonfluent{s}{T}{I} for every state $s \in I$. To do so, we
need to extend the notion of reachability to a notion of coreachability and
then generalize \thmref{IclosureEquivalentIconfluence}. Two states $s_1, s_2
\in I$ are \defword{coreachable} with respect to a set of transactions $T$ and
an invariant $I$, abbreviated \defword{\TIcoreachable}, if there exists some
state $s_0 \in I$ such that $s_1$ and $s_2$ are both \sTIreachable{}.

@@

  Applying \algoref{InteractiveDecisionProcedure}, \IsIclosed{} returns false
  with the states $s_1 = (1, 0, 0), (0, 1, 0)$ and $s_2 = (1, 0, 0), (0, 0,
  1)$. Both are reachable, so $O$ is not \sTIconfluent{} and
  \algoref{InteractiveDecisionProcedure} returns false.  The culprit is
  concurrent decrements, which we can forbid in a simple one-segment
  segmentation $\Sigma = (I, T^+)$ where $T^+$ consists only of increment
  transactions. Applying \algoref{ArbitraryStartInteractiveDecisionProcedure},
  \IsIclosed{} again returns false with the same states $s_1$ and $s_2$. This time,
  however, the user recognizes that the two states are not
  \ticoreachable{T^+}{I}. The user refines $NR$ with the observation that two
  states are coreachable if and only if they have the same values of $n_1, n_2,
  n_3$. After this, \IsIclosed{} (and thus \textsc{Helper}) returns true, and
  \algoref{ArbitraryStartInteractiveDecisionProcedure} terminates.
\end{example}
